---
title: "Vertical integration trend"
author: "Lucy Kim"
date: "8/23/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

source("/Users/kunheekim/Dropbox/Wharton/Research/Labor/code/summarySE.R")
require(devtools)
require(digest)
library(plyr)
library(ggplot2)
library(lubridate)
require(Hmisc)
library(pastecs)
library(zoo) # date
library(plm)
library(gplots)
library(apsrtable)
library("reshape2")
library(readr)
library(reshape)
library(gtable)
library(grid)
library(data.table)

theme_set(theme_bw(base_size=12))
```

## Load data
```{r}
df <- read.csv("/Users/kunheekim/Dropbox/Research/VI/vertical-integration/costreport_hosp/data/hosp_vi.csv")

summary(df$pac)

#reorder categories
df$pac8 <- factor(df$pac, levels=c("hha", "snf", "swbsnf", "irf", "ipf","hospice", "nf", "swbnf"), labels=c("HHA", "SNF", "Swing beds-SNF", "IRF", "IPF", "Hospice", "NF", "Swing beds-NF"))
```

## Check quick descriptive stats: # general short-term hospitals, Mean % PAC VI over time

# short-term hospitals
```{r}
# subset to prov_num, fyear & find unique values
vv <- c("prov_num", "fyear", "vi")
df2 <- subset(df, pac=="hha")
df2 <- df2[vv]
df2 <- unique(df2)

# bar graph
ggplot(df2, aes(x=factor(fyear))) +
  geom_bar(alpha=0.5) +
  labs(title="Number of general short-term hospitals by year", 
        x="Year",
        y="Number of hospitals",
        caption="Note: The fiscal year reported for each cost reporting period is used.") +
    theme_bw(base_size = 13) +
    theme(axis.text.x = element_text(angle=45, vjust=0.6))

ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/numhosp.pdf", width=15, height=10, units="cm")  

# add the number of hospitals vi with HHA
ggplot(df2, aes(x=factor(fyear))) +
  geom_bar(aes(fill=factor(vi)))

df2 <- ddply(df, .(pac8, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))

ggplot(df2, aes(x=factor(fyear), y=vi, colour=pac8, group=pac8)) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   

```

Mean % PAC VI over time with each type across all hospital-years
```{r}
vipct <- ddply(df, .(pac8), summarise, M=100*mean(vi, na.rm=TRUE))
vipct
arrange(vipct, desc(M)) 
```

% PAC VI over time with each type, by CY; plot the trend
```{r}
# df2 <- subset(df, pac=="hha" | pac=="hospice" | pac=="irf" | pac=="snf" )
# 
# #reorder categories
# df2$pac4 <- factor(df2$pac, levels=c("hha", "irf", "snf", "hospice"), labels=c("HHA", "IRF", "SNF", "Hospice"))
# 
# df3 <- ddply(df2, .(pac4, cy), summarise, vi=100*mean(vi, na.rm=TRUE))

df2 <- ddply(df, .(pac8, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))

ggplot(df2, aes(x=factor(fyear), y=vi, colour=pac8, group=pac8)) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom", 
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/vitrend.pdf", width=20, height=10, units="cm")  
```

## VI trend by hospital characteristics: urban, bed size, teaching, ownership type
```{r}
# restrict to 4 types of PAC
df2 <- subset(df, pac=="hha" | pac=="swbsnf" | pac=="irf" | pac=="snf" )

#reorder categories
df2$pac4 <- factor(df2$pac, levels=c("hha", "snf", "swbsnf", "irf"), labels=c("HHA", "SNF", "Swing beds-SNF", "IRF"))
```

urban vs rural
```{r}
summary(df2$urban)

df3 <- ddply(df2, .(urban, pac4, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))
df3 <- subset(df3, is.na(urban)==0)
df3$urban <- factor(df3$urban, levels=c(0,1), labels=c("Rural", "Urban"))
summary(df3$urban)

ggplot(df3, aes(x=factor(fyear), y=vi, colour=pac4, group=pac4)) + facet_grid(.~urban) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
       subtitle="By urban/rural hospitals",
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom",
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/vitrend_urban.pdf", width=20, height=10, units="cm")  
```

bed size
```{r}
summary(df2$size)

df3 <- ddply(df2, .(size, pac4, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))
df3 <- subset(df3, is.na(size)==0)
df3$size <- factor(df3$size, levels=c(1,2,3), labels=c("Beds 1-100", "Beds 101-500", "Beds 501+"))
summary(df3$size)

ggplot(df3, aes(x=factor(fyear), y=vi, colour=pac4, group=pac4)) + facet_grid(.~size) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
       subtitle="By size of hospitals",
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom",
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/vitrend_size.pdf", width=20, height=10, units="cm")  
```

teaching
```{r}
summary(df2$teaching)

df3 <- ddply(df2, .(teaching, pac4, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))
df3 <- subset(df3, is.na(teaching)==0)
df3$teaching <- factor(df3$teaching, levels=c(0,1), labels=c("Non-teaching", "Teaching"))
summary(df3$teaching)

ggplot(df3, aes(x=factor(fyear), y=vi, colour=pac4, group=pac4)) + facet_grid(.~teaching) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
       subtitle="By teaching status",
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom",
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/vitrend_teaching.pdf", width=20, height=10, units="cm")  
```

ownership type
```{r}
df2$owner3 <- factor(ifelse(df2$own_fp==1, 1, ifelse(df2$own_np==1, 2, 3)), labels=c("For-profit", "Nonprofit", "Government"))

summary(df2$owner3)

df3 <- ddply(df2, .(owner3, pac4, fyear), summarise, vi=100*mean(vi, na.rm=TRUE))
df3 <- subset(df3, is.na(owner3)==0)
summary(df3$owner3)

ggplot(df3, aes(x=factor(fyear), y=vi, colour=pac4, group=pac4)) + facet_grid(.~owner3) +
  geom_point() +
  geom_line() +
  labs(title="Percent of hospitals vertically integrated with post-acute care (PAC)", 
       subtitle="By ownership type",
        x="Year",
        y="Percent",
        colour="PAC",
        caption="Note: Sample of general short-term hospitals") +
  theme_bw(base_size = 13) +
  theme(legend.position="bottom",
        axis.text.x = element_text(angle=45, vjust=0.6)) +
  guides(fill=guide_legend(nrow=1, byrow=TRUE))   
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/vitrend_owner3.pdf", width=20, height=10, units="cm")  
```

## Distribution of # home health episodes, # SNF days, # Swing bed-SNF days over time
HH episodes - standard
```{r}
df2 <- subset(df, pac=="hha" & fyear >= 2010)
summary(df2$totepi_out)
df2$totepi <- df2$totepi_st + df2$totepi_out

# count # hospitals to see if 2010 has incomplete data - nope
# df2 <- df2[vv]
# df2 <- unique(df2)
# df2$one <- c(1)
# ddply(df2, .(fyear), summarise, num=sum(one))

p0 <- ggplot(df2, aes(x = factor(fyear), y = totepi_st)) +
  geom_boxplot()

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$totepi_st)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
    labs(title="Number of home health episodes by year", 
       subtitle="Standard episodes",
        x="Year",
        y="Number of episodes",
        caption="Note: Sample of general short-term hospitals VI with HHA") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepitrend_st.pdf", width=20, height=10, units="cm")  

```

HH episodes - outlier
```{r}
p0 <- ggplot(df2, aes(x = factor(fyear), y = totepi_out)) +
  geom_boxplot() 

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$totepi_out)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
  labs(title="Number of home health episodes by year", 
       subtitle="Outlier episodes",
        x="Year",
        y="Number of episodes",
        caption="Note: Sample of general short-term hospitals VI with HHA") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepitrend_out.pdf", width=20, height=10, units="cm")  

```

HH episodes - total
```{r}
p0 <- ggplot(df2, aes(x = factor(fyear), y = totepi)) +
  geom_boxplot()

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$totepi)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
    labs(title="Number of home health episodes by year", 
       subtitle="All episodes",
        x="Year",
        y="Number of episodes",
        caption="Note: Sample of general short-term hospitals VI with HHA") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepitrend.pdf", width=20, height=10, units="cm")  

```

SNF days
```{r}
df2 <- subset(df, pac=="snf" & fyear >= 2010)
summary(df2$snfdays)

p0 <- ggplot(df2, aes(x = factor(fyear), y = snfdays)) +
  geom_boxplot()

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$snfdays)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
    labs(title="Number of SNF days by year", 
        x="Year",
        y="Number of SNF days",
        caption="Note: Sample of general short-term hospitals VI with SNF") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/snfdaystrend.pdf", width=20, height=10, units="cm")  
```

Swing bed-SNF days
```{r}
df2 <- subset(df, pac=="swbsnf" & fyear >= 2010)
summary(df2$swbsnfdays)

p0 <- ggplot(df2, aes(x = factor(fyear), y = swbsnfdays)) +
  geom_boxplot()

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$swbsnfdays)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
    labs(title="Number of Swing bed-SNF days by year", 
        x="Year",
        y="Number of Swing bed-SNF days",
        caption="Note: Sample of general short-term hospitals VI with Swing bed-SNF") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/swbsnfdaystrend.pdf", width=20, height=10, units="cm")  
```

Total SNF days
```{r}
df2 <- subset(df, (pac=="swbsnf" | pac=="snf") & fyear >= 2010)
summary(df2$totsnfdays)

p0 <- ggplot(df2, aes(x = factor(fyear), y = totsnfdays)) +
  geom_boxplot()

# compute lower and upper whiskers
ylim1 <- boxplot.stats(df2$totsnfdays)$stats[c(1, 5)]

# scale y limits based on ylim1
p0 + coord_cartesian(ylim = ylim1*1.05) +
    labs(title="Total number of SNF days by year", 
        x="Year",
        y="Number of SNF days",
        caption="Note: Sample of general short-term hospitals VI with SNF or Swing bed-SNF") +
  theme_bw(base_size = 13)
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/totsnfdaystrend.pdf", width=20, height=10, units="cm")  
```

## Distribution of total # home health episodes, # SNF days, # Swing bed-SNF days in hospital over time
aggregate across all hospitals for each FY

### HHA
```{r}
df2 <- subset(df, pac=="hha" & fyear >= 2010)

df3 <- ddply(df2, .(fyear), summarise, st = sum(totepi_st, na.rm=TRUE), out = sum(totepi_out, na.rm=TRUE))

df3$totepi <- df3$st + df3$out

# standard episodes
ggplot(df3, aes(x=factor(fyear), y=st/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
  labs(title="Total number of home health episodes in VI hospitals by year", 
       subtitle="Standard 60-day home health episodes",
        x="Year",
        y="Number of home health episodes (1000s)",
        caption="Note: I used the sample of hospitals V.I. with HHAs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepi_st.pdf", width=15, height=10, units="cm")  

# outlier episodes
ggplot(df3, aes(x=factor(fyear), y=out/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
  labs(title="Total number of home health episodes in VI hospitals by year", 
       subtitle="Outlier 60-day home health episodes",
        x="Year",
        y="Number of home health episodes (1000s)",
        caption="Note: I used the sample of hospitals V.I. with HHAs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepi_out.pdf", width=15, height=10, units="cm")  


# total episodes
ggplot(df3, aes(x=factor(fyear), y=totepi/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
  labs(title="Total number of home health episodes in VI hospitals by year", 
       subtitle="All 60-day home health episodes",
        x="Year",
        y="Number of home health episodes (1000s)",
        caption="Note: I used the sample of hospitals V.I. with HHAs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/hhepi_all.pdf", width=15, height=10, units="cm")  

```

### SNF
```{r}
df2 <- subset(df, (pac=="swbsnf" | pac=="snf") & fyear >= 2010)

df3 <- ddply(df2, .(fyear), summarise, snfdays = sum(snfdays, na.rm=TRUE), swbsnfdays = sum(swbsnfdays, na.rm=TRUE), totsnfdays = sum(totsnfdays, na.rm=TRUE))
df3

# SNF days
ggplot(df3, aes(x=factor(fyear), y=snfdays/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
  labs(title="Total number of SNF days in VI hospitals by year", 
        x="Year",
        y="Number of SNF days (1000s)",
        caption="Note: I used the sample of hospitals V.I. with SNFs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/snfdays.pdf", width=15, height=10, units="cm")  

# outlier episodes
ggplot(df3, aes(x=factor(fyear), y=swbsnfdays/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
  labs(title="Total number of swing bed-SNF days in VI hospitals by year", 
        x="Year",
        y="Number of swing bed-SNF days (1000s)",
        caption="Note: I used the sample of hospitals V.I. with swing bed-SNFs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/swbsnfdays.pdf", width=15, height=10, units="cm")  


# total SNF days
ggplot(df3, aes(x=factor(fyear), y=totsnfdays/1000)) +
  geom_bar(stat="identity", alpha=0.5) +
 labs(title="Total number of SNF and swing bed-SNF days in VI hospitals by year", 
        x="Year",
        y="Number of SNF and swing bed-SNF days (1000s)",
        caption="Note: I used the sample of hospitals V.I. with SNFs.") +
    theme_bw(base_size = 13) 
ggsave("/Users/kunheekim/Dropbox/Research/VI/gph/totsnfdays.pdf", width=15, height=10, units="cm")  
```